Thesis outline

### 2017-07-19 KellyDouglass/Thesis/Thesis_sections/Introduction.tex
Fixed typos

Large galaxy surveys such as the Sloan Digital Sky Survey \citep[SDSS;][]
{York00} have revealed a non-uniform distribution of galaxies throughout 
the universe.  Taking on a shape similar to that of a sponge-like topology 
\citep{Gott98} or a three-dimensional cosmic web \citep{Bond96}, galaxies clump 
together in clusters and along filaments, leaving void regions between these 
large-scale structures.  Evidence of this distribution can be seen in Fig. 
\ref{fig:SDSS_map} for galaxies in the SDSS Data Release 7 \citep[SDSS DR7;][]
{Abazajian09}.  Based on these observations, dark matter simulations have been 
constructed which successfully reproduce the same large-scale structure.  If we 
start with a mostly uniform distribution of dark matter at the Big Bang with 
quantum mechanical perturbations, Fig. \ref{fig:DMsim} outlines the evolution of 
that dark matter up through the present.  These snapshots from the Millenium 
Simulation project \citep{Springel05} show that small perturbations in the 
initial distribution of dark matter are amplified as the universe expands.  
Gravity causes the slightly overdense regions to collapse while simultaneously 
causing the underdense regions to expand.  Due to dark matter's gravitational 
attraction, we believe that the baryonic mattter (matter which interacts 
electromagnetically) will trace the dark matter distribution, resulting in the 
galaxy distribution we observe today.

@@

% What do we already know about the environmental influence?
Observational studies of void galaxies have included investigation of 
photometric properties such as luminosity \citep{Hoyle05,Croton05,Moorman15}, 
color and morphological type \citep{Grogin00,Rojas04,Patiri06,Park07,
vonBendaBeckmann08,Hoyle12}, star formation rates estimated from optical 
spectroscopy and UV photometry \citep{Rojas05,Moorman15,Beygu16}, and gas 
content \citep{Kreckel12,Moorman16,Jones16}.  When compared to galaxies in 
denser regions, void galaxies tend to be fainter, of late morphological types, 
bluer, forming stars at higher rates per unit stellar mass, and more gas rich.

@@

In particular, we study the effects of the large-scale environment on the 
formation and evolution of dwarf galaxies.  Fig. \ref{fig:Mr_SDSS} shows the 
distribution of galaxies by their absolute magnitudes detected in SDSS DR7.  
Defined to be galaxies with absolute magnitudes fainter than -17 ($M_r > -17$), 
the low stellar masses of dwarf galaxies correspond to more shallow 
gravitational potential wells.  This causes any environmental effects to have a 
more significant influence on dwarf galaxies than on galaxies with larger 
stellar masses.  In addition, studying void dwarf galaxies will complement 
previous studies of dwarfs in groups and clusters because the assembly histories 
of low-mass galaxies are predicted to be very different \citep[e.g.,][]{Gao07,
Lackner12}.  Observations to date also show that the properties of dwarf 
galaxies vary dramatically with the environment \citep[e.g.,][]{Ann08,Geha12}.

@@

The ion transitions observed in the optical part of the spectrum (where SDSS DR7 
operates) consist of forbidden transitions.  As explained in detail in Section 
\ref{sec:physics}, forbidden transitions have much longer lifetimes than the 
allowed electric dipole electron transitions.  These transitions strongly depend 
on the temperature and density of the electron gas, because the long lifetimes 
allow the atoms to easily collisionally de-excite.  By taking the ratio of the 
[\ion{O}{3}] $\lambda$4363 auroral line to the [\ion{O}{3}] 
$\lambda \lambda$4959,5007 doublet, we can get an estimate of the temperature of 
the gas.  These lines are highlighted on the example SDSS DR7 spectrum shown in 
Fig. \ref{fig:spectrum}.

Oxygen is used as a proxy to measure the metallicity of an \ion{H}{2} region, 
because oxygen is the most abundant element in the universe after hydrogen and 
helium \citep{Emsley11}.  It also has strong emission lines in the visible 
wavelength range, so it is relatively easy to observe.  Oxygen emission is the 
most effective cooling source in an \ion{H}{2} region, so lower metallicities 
correspond to higher temperatures.  There are three main factors which determine 
the strength of an emission line: the gas temperature, the electron density, and 
the relative number of ions in the gas.  It is possible to calculate the number 
ratios for any of the heavy elements with respect to hydrogen once the electron 
temperature and density of the interstellar gas are estimated.

% Outline of Thesis
% Pose the problem - how does the large-scale environment affect galaxy evolution?
We want to understand how the cosmic environment affects the evolution of a 
galaxy and what influence it has on a galaxy's star formation.  To do this, we 
compare the properties of galaxies living in voids with galaxies in denser 
regions in an effort to understand how the properties of the gas and the history 
of star formation in a galaxy depend on the environment.  We then try to infer 
what these results tell us about the dark matter structure and history of the 
galaxy.  In Chapter \ref{ch:Paper1}, we calculate and compare the metallicity of 
135 star-forming dwarf galaxies as a function of their large-scale environment.  
We continue studying this galaxy sample in Chapter \ref{ch:Paper2} by estimating 
their ratios of nitrogen to oxygen and looking at how that depends on the 
large-scale environment.  To expand our dwarf galaxy sample, we derive an 
approximation for the amount of singly-ionized oxygen and repeat our analysis of 
the large-scale environmental influence on the gas-phase chemical abundances of 
1920 star-forming dwarf galaxies in Chapter \ref{ch:Paper3}.  In Chapter 
\ref{ch:smallScaleEnvironment}, we investigate how the dwarf galaxies' 
properties depend on the galaxies' distances to the nearest neighbors and 
groups.  Finally, in an effort to better understand how galaxies evolve from 
blue, star-forming systems to ``red and dead,'' we discover a way to classify 
galaxies into their location on the color-magnitude diagram in Chapter 
\ref{ch:GV}.  We present our conclusions and suggestions for future research in 
Chapter \ref{ch:conclusion}.

>>>>

Large galaxy surveys such as the Sloan Digital Sky Survey \citep[SDSS;][]
{York00} have revealed a non-uniform distribution of galaxies throughout 
the universe.  Taking on a shape similar to that of a sponge-like topology 
\citep{Gott98} or a three-dimensional cosmic web \citep{Bond96}, galaxies clump 
together in clusters and along filaments, leaving void regions between these 
large-scale structures.  Evidence of this distribution can be seen in Fig. 
\ref{fig:SDSS_map} for galaxies in the SDSS Data Release 7 \citep[SDSS DR7;][]
{Abazajian09}.  Based on these observations, dark matter simulations have been 
constructed which successfully reproduce the same large-scale structure.  If we 
start with a mostly uniform distribution of dark matter at the Big Bang 
containing quantum mechanical perturbations, Fig. \ref{fig:DMsim} outlines the 
evolution of that dark matter distribution up through the present epoch.  These 
snapshots from the Millenium Simulation project \citep{Springel05} show that 
small perturbations in the initial distribution of dark matter are amplified as 
the universe expands.  Gravity causes the slightly overdense regions to collapse 
while simultaneously causing the underdense regions to expand.  Due to dark 
matter's gravitational attraction, we believe that the baryonic mattter (matter 
which interacts electromagnetically) will trace the dark matter distribution, 
resulting in the galaxy distribution we observe today.

@@

% What do we already know about the environmental influence?
Observational studies of void galaxies have included investigations of 
photometric properties such as luminosity \citep{Hoyle05,Croton05,Moorman15}, 
color and morphological type \citep{Grogin00,Rojas04,Patiri06,Park07,
vonBendaBeckmann08,Hoyle12}, star formation rates estimated from optical 
spectroscopy and UV photometry \citep{Rojas05,Moorman15,Beygu16}, and gas 
content \citep{Kreckel12,Moorman16,Jones16}.  When compared to galaxies in 
denser regions, void galaxies tend to be fainter, of late morphological types, 
bluer, forming stars at higher rates per unit stellar mass, and more gas rich.

@@

In particular, we study the effects of the large-scale environment on the 
formation and evolution of dwarf galaxies.  Fig. \ref{fig:Mr_SDSS} shows the 
distribution in absolute magnitudes of galaxies detected in SDSS DR7.  Defined 
to be galaxies with absolute magnitudes fainter than -17 ($M_r > -17$), the low 
stellar masses of dwarf galaxies correspond to more shallow gravitational 
potential wells.  This causes any environmental effects to have a more 
significant influence on dwarf galaxies than on galaxies with larger stellar 
masses.  In addition, studying void dwarf galaxies will complement previous 
studies of dwarfs in groups and clusters because the assembly histories of 
low-mass galaxies are predicted to be very different \citep[e.g.,][]{Gao07,
Lackner12}.  Observations to date have also shown that the properties of dwarf 
galaxies vary dramatically with the environment \citep[e.g.,][]{Ann08,Geha12}.

@@

The ion transitions observed in the optical part of the spectrum (where SDSS DR7 
operates) consist of forbidden transitions.  As explained in detail in Section 
\ref{sec:physics}, forbidden transitions have much longer lifetimes than the 
allowed electric dipole electron transitions.  These transitions strongly depend 
on the temperature and density of the electron gas, because the long lifetimes 
allow the atoms to easily collisionally de-excite.  By taking the ratio of the 
[\ion{O}{3}] $\lambda$4363 auroral line to the [\ion{O}{3}] 
$\lambda \lambda$4959,5007 doublet, we can estimate the temperature of the gas.  
These lines are highlighted on the example SDSS DR7 spectrum shown in Fig. 
\ref{fig:spectrum}.

Oxygen is used as a proxy to measure the metallicity of an \ion{H}{2} region 
because it is the most abundant element in the universe after hydrogen and 
helium \citep{Emsley11}.  It also has strong emission lines in the visible 
wavelength range, so it is relatively easy to observe.  Oxygen emission is the 
most effective cooling source in an \ion{H}{2} region, so lower metallicities 
correspond to higher temperatures.  There are three main factors which determine 
the strength of an emission line: the gas temperature, the electron density, and 
the relative number of ions in the gas.  It is possible to calculate the number 
ratio for any of the heavy elements with respect to hydrogen once the electron 
temperature and density of the interstellar gas are estimated.

% Outline of Thesis
% Pose the problem - how does the large-scale environment affect galaxy evolution?
We want to understand how the cosmic environment affects the evolution of a 
galaxy and what influence it has on a galaxy's star formation.  To do this, we 
compare the properties of galaxies living in voids with galaxies in denser 
regions in an effort to understand how the properties of the gas and the history 
of star formation in a galaxy depend on the environment.  We then try to infer 
what these results tell us about the dark matter structure and history of the 
galaxy.  In Chapter \ref{ch:Paper1}, we calculate and compare the metallicity of 
135 star-forming dwarf galaxies as a function of their large-scale environment.  
We continue studying this galaxy sample in Chapter \ref{ch:Paper2} by estimating 
their ratios of nitrogen to oxygen and looking at how this ratio depends on the 
large-scale environment.  To expand our dwarf galaxy sample, we derive an 
approximation for the amount of singly-ionized oxygen and repeat our analysis of 
the large-scale environmental influence on the gas-phase chemical abundances of 
1920 star-forming dwarf galaxies in Chapter \ref{ch:Paper3}.  In Chapter 
\ref{ch:smallScaleEnvironment}, we investigate how the dwarf galaxies' 
properties depend on the galaxies' distances to their nearest neighbors and 
groups.  Finally, in an effort to better understand how galaxies evolve from 
blue, star-forming systems to ``red and dead'' galaxies, we discover a way to 
classify the location of galaxies on the color-magnitude diagram in Chapter 
\ref{ch:GV}.  We present our conclusions and suggestions for future research in 
Chapter \ref{ch:conclusion}.

### 2017-07-19 KellyDouglass/Thesis/Thesis_sections/Paper3.tex
Fixed typos

% Forcus on dwarf galaxies, which are most sensitive to effects of environment
% SDSS allows void catalog (Pan et al.) and identification of statistically-significant samples of dwarf galaxies (Mr > -17) in voids
% Discuss importance of careful use of metallicity (O/H) estimators - commonly used methods not calibrated for low mass galaxies, so we carefully used "direct" method
% Summary of results in Douglass & Vogeley 2017a,b
Environmental effects should be the most obvious on dwarf galaxies, since they 
possess small gravitational potential wells.  As a result, they are more 
sensitive to astrophysical effects such as cosmological reionization, internal 
feedback from supernova and photoheating from star formation, external effects 
from tidal interactions and ram pressure stripping, small-scale details of dark 
matter halo assembly, and properties of dark matter.  The main galaxy sample of 
SDSS DR7 covers a large enough volume to identify over 1000 voids \citep{Pan12} 
along with a statistically-significant sample of dwarf galaxies ($M_r > -17$) in 
voids.  SDSS also provides spectroscopy that permits metallicity estimates of 
this large sample of dwarf galaxies.

@@

% In this paper...
% New approach to O abundance estimation - allows use of larger sample.  Still using "direct" method.
% Note that this work examines dwarf, star-forming galaxies only
% Here we also examine HI properties
% Known influence of environment on morphology already taken into account (well, not exactly because we select on emission lines, not morphology from photometry) - we look only at star-forming galaxies
% Known influence of environment on luminosity already taken into account - we look only at dwarfs
We look to expand on the work by \cite{Douglass17a,Douglass17b} by substantially 
increasing their sample size of dwarf galaxies.  The main limiting factor in 
their sample was due to the required detection of the [\ion{O}{2}] $\lambda$3727 
doublet, which is needed to estimate the amount of singly-ionized oxygen 
present.  We present a new approach to the O$^+$ abundance estimation, which 
removes the need for this emission line.  This calculation is used in 
conjunction with the Direct $T_e$ method to estimate the total gas-phase oxygen 
abundance in galaxies.  We also examine the relationship between the chemical 
abundance and \ion{H}{1} mass of star-forming dwarf galaxies.  For reasons 
described above, this work only examines the chemical evolution of star-forming 
dwarf galaxies.  As a result of this sample, the known influences of the 
environment on the morphology and luminosity have already be taken into account, 
since we concentrate only on star-forming dwarf galaxies.

@@

\begin{figure}
    \centering
    \includegraphics[width=0.75\textwidth]{Images/Paper3/Zlow_v_Zreal_1sig_I06_BPTclass_fits}
    \caption[O$^++$/H versus O/H]{$12 + \log{\text{O}^{++}/\text{H}}$ versus \OH 
    for those galaxies with $M_r > -20$ as calculated with the direct method; 
    the galaxies are colored by their classification in the BPT diagrams 
    \citep[from][]{Brinchmann04}.  Two linear models have been fit to three 
    groups in the sample: star-forming and AGN/composite galaxies; the best fit 
    parameters can be found in Table \ref{tab:ab}.}
    \label{fig:lowVreal}
\end{figure}

@@

    \caption[Coefficients of oxygen abundance fits]{Coefficients for the linear 
    trends (Eqn. \ref{eq:fit}) fit to the SF galaxies (dwarf and those with 
    $M_r > -20$) and AGN and composite galaxies.  With these trends, we can now 
    calculate the total oxygen abundance for a galaxy with knowing only the 
    O$^{++}$/H abundance.}

>>>>

% Forcus on dwarf galaxies, which are most sensitive to effects of environment
% SDSS allows void catalog (Pan et al.) and identification of statistically-significant samples of dwarf galaxies (Mr > -17) in voids
% Discuss importance of careful use of metallicity (O/H) estimators - commonly used methods not calibrated for low mass galaxies, so we carefully used "direct" method
% Summary of results in Douglass & Vogeley 2017a,b
Environmental effects should be the most obvious on dwarf galaxies, since they 
possess small gravitational potential wells.  As a result, they are more 
sensitive to astrophysical effects such as cosmological reionization, internal 
feedback from supernovae and photoheating from star formation, external effects 
from tidal interactions and ram pressure stripping, small-scale details of dark 
matter halo assembly, and properties of dark matter.  The main galaxy sample of 
SDSS DR7 covers a large enough volume to identify over 1000 voids \citep{Pan12} 
along with a statistically-significant sample of dwarf galaxies ($M_r > -17$) in 
voids.  SDSS also provides spectroscopy that permits metallicity estimates of 
this large sample of dwarf galaxies.

@@

% In this paper...
% New approach to O abundance estimation - allows use of larger sample.  Still using "direct" method.
% Note that this work examines dwarf, star-forming galaxies only
% Here we also examine HI properties
% Known influence of environment on morphology already taken into account (well, not exactly because we select on emission lines, not morphology from photometry) - we look only at star-forming galaxies
% Known influence of environment on luminosity already taken into account - we look only at dwarfs
We look to expand on the work by \cite{Douglass17a,Douglass17b} by substantially 
increasing their sample size of dwarf galaxies.  The main limiting factor in 
their sample was due to the required detection of the [\ion{O}{2}] $\lambda$3727 
doublet, which is needed to estimate the amount of singly-ionized oxygen 
present.  We present a new approach to the O$^+$ abundance estimation, which 
removes the need for this emission line.  This calculation is used in 
conjunction with the Direct $T_e$ method to estimate the total gas-phase oxygen 
abundance in galaxies.  We also examine the relationship between the chemical 
abundance and \ion{H}{1} mass of star-forming dwarf galaxies.  For reasons 
described above, this work only examines the chemical evolution of star-forming 
dwarf galaxies.  As a result of this sample being limited to only star-forming 
galaxies, the known influences of the environment on the morphology and 
luminosity have already be taken into account.

@@

\begin{figure}
    \centering
    \includegraphics[width=0.75\textwidth]{Images/Paper3/Zlow_v_Zreal_1sig_I06_BPTclass_fits}
    \caption[O$^{++}$/H versus O/H]{$12 + \log{\text{O}^{++}/\text{H}}$ versus 
    \OH for those galaxies with $M_r > -20$ as calculated with the direct 
    method; the galaxies are colored by their classification in the BPT diagrams 
    \citep[from][]{Brinchmann04}.  Two linear models have been fit to three 
    groups in the sample: star-forming and AGN/composite galaxies; the best fit 
    parameters can be found in Table \ref{tab:ab}.}
    \label{fig:lowVreal}
\end{figure}

@@

    \caption[Coefficients of O$^+$ approximation]{Coefficients for the linear 
    trends (Eqn. \ref{eq:fit}) fit to the SF galaxies (dwarf and those with 
    $M_r > -20$) and AGN and composite galaxies.  With these trends, we can now 
    calculate the total oxygen abundance for a galaxy with knowing only the 
    O$^{++}$/H abundance.}

### 2017-07-19 KellyDouglass/Thesis/preamble.tex
Fixed typos

% Advisor
I would like to begin by thanking my advisor, Prof. Michael Vogeley, for being a 
fantastic advisor and role model.  Thank you for helping me expand my knowledge 
and research skills over the last six years.  And thank you for giving me the 
opportunity to help advise students.  I would like to thank our collaborator 
Renyue Cen for his help in the theoretical interpretation of these results, and 
for confirming that our explanations were not completely ridiculous.  To my 
committee members Profs. Gordon Richards, Steve McMillan, Masao Sako, and 
Michelle Dolinksi --- thank you for your time and guidance throughout the years.  
And a big shout-out to my advisees: Daniele Schneider, Jinfu Dai, Brean 
Prefontaine, and Salvatore Zerbo.  Thank you for all your hard work!

% Grad students & PLBD
Thank you to all the graduate students in the Drexel Physics department for the 
wonderful, supportive, collaborative community.  You helped make grad school so 
much more bearable (and almost enjoyable, if I dare say).  To my physics boys 
Justin, Matt, and Matt: we made it!  I would be remiss in not acknowledging my 
office mates over the last few years, particularly Josh, Jackie, Justin, 
Crystal, Austen, and Vish, for help with code, ideas, and keeping the moral up.  
And, of course, thank you to all the members of PLBD for providing me an outlet 
from physics.  You guys are the best!

% Family
Of course, none of this would be possible without the infinite love and support 
from my family.  Thank you Dad, Mom, Kelly, and Ren\'{e}e for always pushing me 
to work my hardest and do my best.  Thank you for challenging me in so many 
ways.  I love you guys, and it means so much that you are here today!

@@

% Papers 1-3
We investigate how the cosmic environment affects galaxy evolution in the 
Universe by studying gas-phase chemical abundances and other galaxy properties 
as a function of the large-scale environment and local density of galaxies.  
Using spectroscopic observations from the Sloan Digital Sky Survey Data Release 
7, we estimate the oxygen and nitrogen abundances of 993 star-forming void dwarf 
galaxies and 759 star-forming dwarf galaxies in denser regions.  We use the 
Direct $T_e$ method for calculating the gas-phase chemical abundances in the 
dwarf galaxies because it is best suited for low metallicity, low mass galaxies.  
A substitute for the [\ion{O}{2}] $\lambda$3727 doublet is developed, permitting 
oxygen abundance estimates of SDSS dwarf galaxies at all redshifts with the 
Direct $T_e$ method.  We find that star-forming void dwarf galaxies have 
slightly higher oxygen abundances than star-forming dwarf galaxies in denser 
environments, but we find that void dwarf galaxies have slightly lower nitrogen 
abundances and lower N/O ratios than galaxies in denser regions.  
% Small-scale enivronment
At smaller scales, we find that only the presence of a neighboring galaxy within 
0.05 \hMpc or 0.05$r_{vir}$, or the presence of a group within 0.1 \hMpc, 
influences a dwarf galaxy's evolution.  Dwarf galaxies within 0.05 \hMpc or 
0.05$r_{vir}$ of another galaxy tend to be bluer, have higher sSFRs, and have 
higher oxygen and nitrogen abundances than average.  In contrast, galaxies 
within 0.1 \hMpc of the center of the closest group are redder, have lower 
oxygen abundances, and have higher N/O ratios than average.
% GV
We also investigate how a galaxy transitions through the color-magnitude 
diagram, evolving from a blue, star-forming spiral or irregular galaxy in the 
blue sequence to a red elliptical galaxy in the red cloud through the green 
valley.  We discover that combining a galaxy's color, color gradient, and 
inverse concentration index defines a galaxy's location on the color-magnitude 
diagram.  The results indicate that there is a higher fraction of dwarf galaxies 
in denser regions than void dwarf galaxies in the green valley.
% Conclusions
From these analyses, we surmise that void dwarf galaxies experience delayed star 
formation as predicted by the $\Lambda$CDM cosmology.  We also conjecture that 
cosmic downsizing corresponds to a shift towards star formation in both lower 
mass objects and void regions closer to the present epoch.  We present evidence 
that void dwarf galaxies may have a higher ratio of dark matter halo mass to 
stellar mass when compared to dwarf galaxies in denser environments.

>>>>

% Advisor
I would like to begin by thanking my advisor, Prof. Michael Vogeley, for being a 
fantastic advisor and role model.  Thank you for helping me expand my knowledge 
and research skills over the last six years.  And thank you for giving me the 
opportunity to help advise students.  I would also like to thank our 
collaborator, Renyue Cen, for his help in the theoretical interpretation of 
these results and for confirming that our explanations are not completely 
ridiculous.  To my committee members: Profs. Gordon Richards, Steve McMillan, 
Masao Sako, and Michelle Dolinski --- thank you for your time and guidance 
throughout the years.  And a big shout-out to my advisees: Daniele Schneider, 
Jinfu Dai, Brean Prefontaine, and Salvatore Zerbo.  Thank you for all your hard 
work!

% Grad students & PLBD
Thank you to all the graduate students in the Drexel Physics department for the 
wonderful, supportive, collaborative community.  You helped make grad school so 
much more bearable (and almost enjoyable, if I dare say).  To my physics boys 
Justin, Matt, and Matt: we made it!  I would also be remiss in not acknowledging 
my office mates over the last few years, particularly Josh, Jackie, Justin, 
Crystal, Austen, and Vish, for help with code, ideas, and keeping up the moral.  
And, of course, thank you to all the members of PLBD for providing me an outlet 
from physics.  You guys are the best!

% Family
None of this would have been possible without the infinite love and support from 
my family.  Thank you Dad, Mom, Kelly, and Ren\'{e}e for always pushing me to 
work my hardest and to do my best.  Thank you for challenging me in so many 
ways.  I love you guys, and it means so much that you are here today!

@@

% Papers 1-3
We investigate how the cosmic environment affects galaxy evolution in the 
Universe by studying gas-phase chemical abundances and other galaxy properties 
as a function of the large-scale environment and local density of galaxies.  
Using spectroscopic observations from the Sloan Digital Sky Survey Data Release 
7, we estimate the oxygen and nitrogen abundances of 993 star-forming void dwarf 
galaxies and 759 star-forming dwarf galaxies in denser regions.  We use the 
Direct $T_e$ method for calculating the gas-phase chemical abundances in the 
dwarf galaxies because it is best suited for low metallicity, low mass galaxies.  
A substitute for the [\ion{O}{2}] $\lambda$3727 doublet is developed, permitting 
oxygen abundance estimates of SDSS dwarf galaxies at all redshifts with the 
Direct $T_e$ method.  We find that star-forming void dwarf galaxies have 
slightly higher oxygen abundances than star-forming dwarf galaxies in denser 
environments, but we find that void dwarf galaxies have slightly lower nitrogen 
abundances and lower N/O ratios than galaxies in denser regions.  
% Small-scale enivronment
At smaller scales, we find that only the presence of a neighboring galaxy within 
0.05 \hMpc or 0.1$r_{vir}$, or the presence of a group within 0.05 \hMpc, 
influences a dwarf galaxy's evolution.  Dwarf galaxies within 0.05 \hMpc or 
0.1$r_{vir}$ of another galaxy tend to be bluer, have higher sSFRs, have higher 
oxygen abundances, and have lower N/O ratios than average.  In contrast, 
galaxies within 0.05 \hMpc of the center of the closest group have lower oxygen 
and nitrogen abundances than average.
% GV
We also investigate how a galaxy transitions through the color-magnitude 
diagram, evolving from a blue, star-forming spiral or irregular galaxy in the 
blue sequence to a red elliptical galaxy in the red cloud through the green 
valley.  We discover that combining a galaxy's color, color gradient, and 
inverse concentration index determines a galaxy's location on the 
color-magnitude diagram.  The results indicate that, in the green valley, there 
is a lower fraction of void dwarf galaxies than dwarf galaxies in denser 
regions.
% Conclusions
From these analyses, we surmise that void dwarf galaxies experience delayed star 
formation as predicted by the $\Lambda$CDM cosmology.  We also conjecture that 
cosmic downsizing corresponds to a shift towards star formation in both lower 
mass objects and void regions closer to the present epoch.  We present evidence 
that void dwarf galaxies may have a higher ratio of dark matter halo mass to 
stellar mass when compared to dwarf galaxies in denser environments.

### 2017-07-19 KellyDouglass/Thesis/simulations.tex
Added acknowledgments and dedication
Fixed typos

\chapter[Simulations]{Simulations of dwarf galaxy formation and evolution}

Numerous simulations have been performed over the years in an attempt to 
understand the formation and evolution of our universe.  As observers, it is 
important to connect our observations with the theory in order to grow our ideas 
about the universe.

@@

% Hierarchical formation of halos
It is impossible to directly observe the formation of a galaxy.  Based on 
detected merging galaxies, the astronomical community has surmised that galaxies 
have increased their mass largely due to the merging of smaller galaxies.  
$\Lambda$CDM simulations of hierarchical galaxy formation by \cite{deRossi07} 
find that the growth of systems by aggregation is responsible for the 
mass-metallicity relation.  Less massive systems tend to increase their stellar 
mass by either gas-rich mergers or secular evolution, resulting in a stronger 
correlation between stellar mass and metallicity.  Evidence of this is seen in 
the mass-metallicity relation of \cite{Tremonti04}, where there is little 
relationship between stellar mass and the metallicity for massive systems, but 
at intermediate and lower masses the correlation is strong between the two 
quantities.

% ISM - inflows and outflows
The inflow and outflow of gas in galaxies are aspects of galaxy evolution that 
are not yet well understood.  This is especially important when studying dwarf 
galaxies, since their gravitational potential wells may be shallow enough to be 
strongly influenced by stellar winds and/or supernovae.  Simulations by 
\cite{Marcolini04} find that when ram pressure from the intergalactic medium 
(IGM) is comparable to the thermal pressure of the central interstellar medium 
(ISM), stripping and superwind influence each other and increase the gas removal 
rate.  They find that the amount of metal-rich ejecta is sensitive to the ram 
pressure.  
% supernova
Simulations by \cite{Power14} and \cite{Melioli15} show that supernovae contain 
sufficient energy to unbind the gas in a low mass halo.  \cite{Hu16} show that 
supernova-driven galactic outflows push metal-rich gas into the halo.  A small 
fraction of the gas eventually escapes the halo, while most falls back onto the 
disc.  This results in the halo metallicity being about 20\% higher than the 
disc metallicity.  Likewise, \cite{Muratov17} find that almost all metals 
produced in a Type II supernova are ejected from the galaxy.
% star formation
Unlike the supernovae, \cite{Melioli15} finds that the ISM material does not 
have a strong likelihood of being expelled from a galaxy due to star formation.  
In contrast, \cite{Muratov15} finds that a large portion of material is ejected 
in galactic outflows after a bust of star formation, which collects in the 
circumgalactic medium (CGM) and is sometimes recycled in later star formation 
episodes.  In galaxies with $M_h < 10^{12} M_\odot$, a fraction of material is 
lost to the IGM.

% Metallicity
Numerical simulations that study the properties of the ISM in an isolated, 
star-forming galaxy find that stellar feedback slowly increases the disc 
metallicity \citep{Hu16}.  The majority of outflows are enriched winds, which 
reduces the metallicity of the ISM.  In dwarf galaxies at low redshifts, these 
outflows to the CGM are dominated by metal-poor gas \citep{Muratov17}.  While 
galaxies retain most of the metals they produce, a large fraction is in the CGM.  
By combining our observations with the results of these simulations, we can 
begin to understand how star formation and supernovae influence a dwarf galaxy's 
gas content.

@@

\cite{Cen11} studied cosmic downsizing with high-resolution large-scale 
hydrodynamic galaxy formation simulations based on the $\Lambda$CDM cosmology.  
He finds that cosmic downsizing is part of a trend where the sSFR is a function 
of halo mass such that lower-mass galaxies have higher sSFRs.  The formation of 
large halos (groups and clusters) and the large-scale structure causes cosmic 
gas to heat beyond a critical temperature at which the gas's entropy is too high 
to cool to continue feeding the galaxies and their star formation.  As the 
surrounding gas in the dense regions becomes heated beyond the critical limit, 
the sSFR of the affected galaxies decreases and the galaxies transition from the 
blue sequence to the red cloud.  In the void environment, this heating does not 
occur, and so galaxies in the voids maintain a high sSFR in the present epoch.  
While this is the overall trend, there still exists some galaxies at $z=0$ which 
have a high sSFR but reside in the more dense environments.

>>>>

\chapter[Simulations]{Simulations of Dwarf Galaxy Formation and Evolution}

Numerous simulations have been performed over the years in an attempt to 
understand the formation and evolution of our universe.  As observers, it is 
important to connect our observations with the theory in order to expand our 
ideas about the universe.

@@

% Hierarchical formation of halos
Due to the vast time scales over which galaxy formation occurs, it is impossible 
to directly observe the formation of a galaxy.  Based on observed merging 
galaxies, the astronomical community has surmised that galaxies increase their 
mass largely due to the merging of smaller galaxies.  $\Lambda$CDM simulations 
of hierarchical galaxy formation by \cite{deRossi07} find that the growth of 
systems by aggregation is responsible for the mass-metallicity relation.  Less 
massive systems tend to increase their stellar mass by either gas-rich mergers 
or secular evolution, resulting in a stronger correlation between stellar mass 
and metallicity.  Evidence of this is seen in the mass-metallicity relation of 
\cite{Tremonti04}, where there is little relationship between stellar mass and 
the metallicity for massive systems, but at intermediate and lower masses the 
correlation is strong between the two quantities.

% ISM - inflows and outflows
The inflow and outflow of gas in galaxies are aspects of galaxy evolution that 
are not yet well understood.  This is especially important when studying dwarf 
galaxies, since their gravitational potential wells may be shallow enough to be 
strongly influenced by stellar winds and/or supernovae.  Simulations by 
\cite{Marcolini04} find that when ram pressure from the intergalactic medium 
(IGM) is comparable to the thermal pressure of the central interstellar medium 
(ISM), stripping and superwinds influence each other and increase the gas 
removal rate.  They find that the amount of metal-rich ejecta is sensitive to 
the ram pressure.  
% supernova
Simulations by \cite{Power14} and \cite{Melioli15} show that supernovae contain 
sufficient energy to unbind the gas in a low mass halo.  \cite{Hu16} show that 
supernova-driven galactic outflows push metal-rich gas into the halo.  A small 
fraction of this gas eventually escapes the halo, while most falls back onto the 
disc.  This results in the halo metallicity being about 20\% higher than the 
disc metallicity.  Likewise, \cite{Muratov17} find that almost all metals 
produced in a Type II supernova are ejected from the galaxy.
% star formation
Unlike the supernovae, \cite{Melioli15} find that the ISM material does not have 
a strong likelihood of being expelled from a galaxy due to star formation.  In 
contrast, \cite{Muratov15} find that a large portion of material is ejected in 
galactic outflows after a bust of star formation, which collects in the 
circumgalactic medium (CGM) and is sometimes recycled in later star formation 
episodes.  In galaxies with $M_h < 10^{12} M_\odot$, a fraction of material is 
lost to the IGM.

% Metallicity
Numerical simulations that study properties of the ISM in isolated, star-forming 
galaxies find that stellar feedback slowly increases the disc metallicity 
\citep{Hu16}.  The majority of outflows are enriched winds, which reduce the 
metallicity of the ISM.  In dwarf galaxies at low redshifts, metal-poor gas 
dominates these outflows to the CGM \citep{Muratov17}.  While galaxies retain 
most of the metals they produce, a large fraction is in the CGM.  By combining 
our observations with the results of these simulations, we can begin to 
understand how star formation and supernovae influence a dwarf galaxy's gas 
content.

@@

\cite{Cen11} studied cosmic downsizing with high-resolution large-scale 
hydrodynamic galaxy formation simulations based on the $\Lambda$CDM cosmology.  
He finds that cosmic downsizing is part of a trend where the sSFR is a function 
of halo mass such that lower-mass galaxies have higher sSFRs.  The formation of 
large halos (groups and clusters) and the large-scale structure causes cosmic 
gas to heat beyond a critical temperature at which the gas's entropy is too high 
to cool to continue feeding the galaxies and their star formation.  As the 
surrounding gas in the dense regions becomes heated beyond the critical limit, 
the sSFR of the affected galaxies decreases and the galaxies transition from the 
blue sequence to the red cloud.  In the void environment, this heating does not 
occur, and so galaxies in the voids maintain a high sSFR in the present epoch.  
While this is the overall trend, there still exist some galaxies at $z=0$ which 
have a high sSFR but reside in the denser environments.
